Merging merges, more or less

### 2015-04-04 2015mergingmerges/section/01-Introduction.tex
contributions

In summary, the purpose of this work is to determine which programs can be executed with no buffering, and offer an efficient compilation strategy for these.

>>>>

In this paper, we present:
\begin{itemize}
\item a kind of deterministic finite automata, for expressing streaming computations with value-dependent rates (\S\ref{s:Machines});
\item some common combinators implemented with such machines (\S\ref{s:Machines:Combinators});
\item invariants required of such machines (\S\ref{s:Machines:Invariants});
\item and an algorithm for merging non-recursive pairs of these machines (\S\ref{s:Merging}).
\end{itemize}
